### 2024-01-05 tesis_Ashish/Chapter5/chapter5.tex
Updated thesis 5 Jan 2024

Table \ref{tab:bad_modules} presents a quantitative summary of malfunctioning or "bad" modules across various periods. BPIX Layer0 has 96 bad modules. As we progress through the various periods in 2022 (from F to D), there is a general trend of increasing bad modules, both for stability and linearity considerations. This suggests that as time progresses, the number of malfunctioning modules tends to grow. The highest number of bad modules for stability is observed in the 2022D period with 1653 bad modules. On the other hand, the 2022D period also has the highest for linearity with 1677 bad modules. The vdM fill has 1693 bad modules, which is slightly higher than those in the 2022D period for stability but slightly less for linearity. There seems to be a consistent observation that for each given period, the number of bad modules under linearity considerations is either equal to or slightly higher than those under stability considerations \cite{bril2023moduleveto}.

@@

Table \ref{table:12_2022} provides a summary of the number of bad pixel modules identified over different combinations of periods (CD, CDE, CDEF, and CDEFG). The results are achieved using a 4\% rms common module veto list. The table is organized into two columns: 'Periods' and 'Bad Modules'. In the 'Periods' column, various combinations of periods are listed, which denote the time intervals during which the luminosity measurements are conducted. The listed combinations - CD, CDE, CDEF, and CDEFG - indicate that the analysis was done over expanding time frames, starting with periods C and D, then extending to include E, followed by F, and finally G. The 'Bad Modules' column provides the total number of bad or unreliable pixel modules identified across the listed combination of periods. For example, 886 bad modules are found over periods C and D, 1106 bad modules over periods C, D, and E \cite{bril2023moduleveto_1}.

@@

%Background subtraction and beam corrections have been applied to the raw data to account for noise.
%Chi2/ndof for all vdM and Imaging Scans:
%Figure \ref{fig:period_bound_51} provide an indication of the quality of the fits to the scan data.
The $\chi^2$ statistic measures the discrepancy between the observed event rates and the values predicted by the double Gaussian fit, while ndof (number of degrees of freedom) accounts for the complexity of the fit. A value of  $\chi^2$/ndof close to 1 can be seen in the statistics box which signifies a good fit. PCC visible cross section is 1076 $\pm$ 0.9 (stat) mb as shown in Fig. \ref{fig:period_bound_105} \cite{bril2023vdmrecalibration}.

@@

Type-2 parameters, derived from a preceding study using Random trigger data, are presumed to remain constant during the year. The fitting template is given by:
\begin{equation}
F(x) = \Sigma_{k=0}^{N_{bcid}} N_k \left[(x-k==0)+\alpha\cdot(x-k==1)+A \cdot e^{-\tau\cdot(x-k-1)}(x-k>=1) \right]
\end{equation}
with $k$ denoting the colliding bunch crossing and $x$ indicating the histogram bin. 2022 PCC afterglow model uses run number 361957 for doing fit to type 1 and type 2 afterglow effect in the PCC raw data as shown in Fig. \ref{fig:period_bound_101}. Model consist of a parameter for type 1 afterglow correcton and exponentially decaying function with two parameters amplitude and decay width to model type 2 afterglow correction. Fit function is summed over all bunch crossings. Fit perfomed for 4 wagon train is shown in Fig.  \ref{fig:period_bound_102} in run 361957 to compute type 2 afterglow amplitude and decay width. The values obtained for type 2 afterglow amplitude and decay parameters are 0.0007915 and 0.00918 respectively \cite{bril2023afterglow}.
%as shown in Table. \ref{table:trains_data}.

@@

PCC instantaneous luminosity provides a measure of the collider's performance and is graphically represented in Fig. \ref{fig:period_bound_1000045}. Each fill in the graph consistently displays a sequence of characteristics related to luminosity. The process initiates with ramp-up periods, where a swift increase in luminosity is evident. This surge is subsequently followed by leveling parts, where luminosity stabilizes and plateaus. As the fill progresses, burn-off parts emerge, marked by a gradual decline in luminosity. Interspersed within the graph are notable, sharp drops to lower luminosity levels, characteristic of emittance scans. As each fill reaches its culmination, pronounced drops are observable, signifying the end of fill events. This cyclical pattern is evident across all fills, underscoring the systematic nature of the process. Integrated luminosity accumulates this data over time. For 2022, the total PCC integrated luminosity is calculated to be 38.61 $fb^{-1}$ \cite{bril2023randomzerobias}.

@@

\item Stability: Stability systematic uncertainties, often stem from time-variable factors such as detector aging, radiation damage, and noise fluctuations. Detectors used in high-energy physics are subject to a harsh radiation environment which can cause performance degradation over time. This degradation, if not accurately accounted for in the models, can introduce systematic uncertainties. %Furthermore, changes in noise levels can lead to overestimation or underestimation of luminosity due to false or missed signals. While data analysis techniques can suppress noise, any residual noise can introduce additional systematic uncertainty.
  The stability systematic uncertainty is quantified by the standard deviation of the luminosity ratio from the best and second-best luminometer. A larger spread in measurements, indicated by a higher standard deviation, represents a greater systematic uncertainty due to temporal shifts in detector performance or environmental conditions. Fig. \ref{fig:stabprof_78} depicts the time evolution of ratio of luminosity values obtained from the PCC and the HFET luminometer. Each point on the x-axis represents a lumi section - a discrete time interval of data collection. The plot shows the variation in luminosity measurements across the data-taking period. This is crucial in calculating the systematic uncertainty related to stability, as any temporal fluctuations in luminosity could potentially indicate a source of uncertainty in the measurements. %The projection of the luminosity ratio. This projection, by condensing the two-dimensional information along the x axis and displaying the distribution of the luminosity measurements, can help identify any variations in the luminosity data that could contribute to systematic uncertainty. A uniform distribution would suggest good stability, while any deviations might point towards potential sources of systematic uncertainty.
Fig. \ref{fig:stabprof1_79} shows the projection of the luminosity ratio using 50 lumi section binning strategy. %By grouping the lumi sections into larger bins, this visualization enables an aggregated view of luminosity data over broader intervals of the data-taking period.

@@

\newpage
\item Linearity: Detectors in high-energy physics experiments can display varying responses at different luminosity levels, leading to non-linear behavior, especially at high luminosities. %This variability is observable in the residuals of PCC luminosity compared to HFOC luminosity.
To quantify the linearity systematic uncertainty, the slope variability of the detector response against luminosity levels can be analyzed. This, combined with the luminosity range, provides a measure of the expected rate variability due to non-linearity, representing the linearity systematic uncertainty. %Non-linear response during fill 8274 and three consecutive fill 8274, 8275 and 8276 is shown in Fig. \ref{fig:kinknon1_} and \ref{fig:kinknon_}.

>>>>

Table \ref{tab:bad_modules} presents a quantitative summary of malfunctioning or "bad" modules across various periods. BPIX Layer0 has 96 bad modules. As we progress through the various periods in 2022 (from F to D), there is a general trend of increasing bad modules, both for stability and linearity considerations. This suggests that as time progresses, the number of malfunctioning modules tends to grow. The highest number of bad modules for stability is observed in the 2022D period with 1653 bad modules. On the other hand, the 2022D period also has the highest for linearity with 1677 bad modules. The vdM fill has 1693 bad modules, which is slightly higher than those in the 2022D period for stability but slightly less for linearity. There seems to be a consistent observation that for each given period, the number of bad modules under linearity considerations is either equal to or slightly higher than those under stability considerations \cite{pas_22}. % \cite{bril2023moduleveto}.

@@

Table \ref{table:12_2022} provides a summary of the number of bad pixel modules identified over different combinations of periods (CD, CDE, CDEF, and CDEFG). The results are achieved using a 4\% rms common module veto list. The table is organized into two columns: 'Periods' and 'Bad Modules'. In the 'Periods' column, various combinations of periods are listed, which denote the time intervals during which the luminosity measurements are conducted. The listed combinations - CD, CDE, CDEF, and CDEFG - indicate that the analysis was done over expanding time frames, starting with periods C and D, then extending to include E, followed by F, and finally G. The 'Bad Modules' column provides the total number of bad or unreliable pixel modules identified across the listed combination of periods. For example, 886 bad modules are found over periods C and D, 1106 bad modules over periods C, D, and E \cite{pas_22}. %\cite{bril2023moduleveto_1}.

@@

%Background subtraction and beam corrections have been applied to the raw data to account for noise.
%Chi2/ndof for all vdM and Imaging Scans:
%Figure \ref{fig:period_bound_51} provide an indication of the quality of the fits to the scan data.
The $\chi^2$ statistic measures the discrepancy between the observed event rates and the values predicted by the double Gaussian fit, while ndof (number of degrees of freedom) accounts for the complexity of the fit. A value of  $\chi^2$/ndof close to 1 can be seen in the statistics box which signifies a good fit. PCC visible cross section is 1076 $\pm$ 0.9 (stat) mb as shown in Fig. \ref{fig:period_bound_105} \cite{pas_22} %\cite{bril2023vdmrecalibration}.

@@

Type-2 parameters, derived from a preceding study using Random trigger data, are presumed to remain constant during the year. The fitting template is given by:
\begin{equation}
F(x) = \Sigma_{k=0}^{N_{bcid}} N_k \left[(x-k==0)+\alpha\cdot(x-k==1)+A \cdot e^{-\tau\cdot(x-k-1)}(x-k>=1) \right]
\end{equation}
with $k$ denoting the colliding bunch crossing and $x$ indicating the histogram bin. 2022 PCC afterglow model uses run number 361957 for doing fit to type 1 and type 2 afterglow effect in the PCC raw data as shown in Fig. \ref{fig:period_bound_101}. Model consist of a parameter for type 1 afterglow correcton and exponentially decaying function with two parameters amplitude and decay width to model type 2 afterglow correction. Fit function is summed over all bunch crossings. Fit perfomed for 4 wagon train is shown in Fig.  \ref{fig:period_bound_102} in run 361957 to compute type 2 afterglow amplitude and decay width. The values obtained for type 2 afterglow amplitude and decay parameters are 0.0007915 and 0.00918 respectively \cite{pas_22}. %\cite{bril2023afterglow}.
%as shown in Table. \ref{table:trains_data}.

@@

PCC instantaneous luminosity provides a measure of the collider's performance and is graphically represented in Fig. \ref{fig:period_bound_1000045}. Each fill in the graph consistently displays a sequence of characteristics related to luminosity. The process initiates with ramp-up periods, where a swift increase in luminosity is evident. This surge is subsequently followed by leveling parts, where luminosity stabilizes and plateaus. As the fill progresses, burn-off parts emerge, marked by a gradual decline in luminosity. Interspersed within the graph are notable, sharp drops to lower luminosity levels, characteristic of emittance scans. As each fill reaches its culmination, pronounced drops are observable, signifying the end of fill events. This cyclical pattern is evident across all fills, underscoring the systematic nature of the process. Integrated luminosity accumulates this data over time. For 2022, the total PCC integrated luminosity is calculated to be 38.61 $fb^{-1}$ \cite{pas_22}. %\cite{bril2023randomzerobias}.

@@

\item Stability: Stability systematic uncertainties, often stem from time-variable factors such as detector aging, radiation damage, and noise fluctuations. Detectors used in high-energy physics are subject to a harsh radiation environment which can cause performance degradation over time. This degradation, if not accurately accounted for in the models, can introduce systematic uncertainties. %Furthermore, changes in noise levels can lead to overestimation or underestimation of luminosity due to false or missed signals. While data analysis techniques can suppress noise, any residual noise can introduce additional systematic uncertainty.
  The stability systematic uncertainty is quantified by the standard deviation of the luminosity ratio from the best and second-best luminometer. A larger spread in measurements, indicated by a higher standard deviation, represents a greater systematic uncertainty due to temporal shifts in detector performance or environmental conditions. Fig. \ref{fig:stabprof_78} depicts the time evolution of ratio of luminosity values obtained from the PCC and the HFET luminometer. Each point on the x-axis represents a lumi section - a discrete time interval of data collection. The plot shows the variation in luminosity measurements across the data-taking period. This is crucial in calculating the systematic uncertainty related to stability, as any temporal fluctuations in luminosity could potentially indicate a source of uncertainty in the measurements. %The projection of the luminosity ratio. This projection, by condensing the two-dimensional information along the x axis and displaying the distribution of the luminosity measurements, can help identify any variations in the luminosity data that could contribute to systematic uncertainty. A uniform distribution would suggest good stability, while any deviations might point towards potential sources of systematic uncertainty.
Fig. \ref{fig:stabprof1_79} shows the projection of the luminosity ratio using 50 lumi section binning strategy \cite{pas_22}. %By grouping the lumi sections into larger bins, this visualization enables an aggregated view of luminosity data over broader intervals of the data-taking period.

@@

\newpage
\item Linearity: Detectors in high-energy physics experiments can display varying responses at different luminosity levels, leading to non-linear behavior, especially at high luminosities. %This variability is observable in the residuals of PCC luminosity compared to HFOC luminosity.
To quantify the linearity systematic uncertainty, the slope variability of the detector response against luminosity levels can be analyzed. This, combined with the luminosity range, provides a measure of the expected rate variability due to non-linearity, representing the linearity systematic uncertainty \cite{pas_22}. %Non-linear response during fill 8274 and three consecutive fill 8274, 8275 and 8276 is shown in Fig. \ref{fig:kinknon1_} and \ref{fig:kinknon_}.
